A Reduced Order Model for Porous Media Flows: Coupling Linear Regression with Principal Component Analysis (PCA) using High-Order Singular Value Decomposition (HOSVD) in Upscaling Calculations for Permeability in Reservoir Simulations

### 2018-12-03 Papers/AppliedMaths2018/Resubmission/Stochastic_Upscaling_UK_AMM_2018b.tex
files to be modified in the next 250min

Figure~\ref{fig:Saturationfield@t=1.15s}(d) also shows an inconsistency with the BaseCase (Fig.~\ref{fig:Saturationfield@t=1.15s}(a)) where it shows phase 1 moving from block $K2$ into $K4$. This inconsistency is with respect to this realization of the PDFCase. Hence, PCA-LinReg Case in Fig.~\ref{fig:Saturationfield@t=1.15s}(e) give the best representation of the BaseCase in \ie Fig.~\ref{fig:Saturationfield@t=1.15s}(a)

@@

Upscaling is a form of reduced order model, and a method of implementing upscaling by coupling linear regression with PCA is introduced in this work. For a 2-D model, SVD is used to decompose the existing permeability field to obtain the PCA space, while HOSVD is used for 3-D models. Within, the PCA space, linear regression (or interpolation) is used to reduce the data in the PCA space. The reduced data in the principal component space is then recombined to form a reduced data of the permeability field.

Results show that the permeability field data reduction can be specifically defined for the PDFCase and the PCA-LinReg Case but not for the ArithMeanCase and the HarmMeanCase. This is because the latter cases will produce the same permeability field irrespective of the upgrid resolution. The PCA-LinReg Case is the only technique that does not require a prior knowledge of blocks with similar permeability values before upscaling. This is a huge advantage as it saves time during the data pre-processing stage, because sorting and calculations for each distinct region is avoided.

>>>>

Figure~\ref{fig:Saturationfield@t=1.15s}d also shows an inconsistency with the BaseCase (Fig.~\ref{fig:Saturationfield@t=1.15s}a) where it shows phase 1 moving from block $K2$ into $K4$. This inconsistency is with respect to this realization of the PDFCase. Hence, PCA-LinReg Case in Fig.~\ref{fig:Saturationfield@t=1.15s}e gives the best representation of the BaseCase in \ie Fig.~\ref{fig:Saturationfield@t=1.15s}a.

\red{HOSVD????HOSVD????HOSVD????HOSVD????HOSVD????}

@@

Upscaling is a form of reduced order model. A method of implementing upscaling by coupling linear regression with PCA is introduced in this work. For a 2-D model, SVD is used to decompose the existing permeability field to obtain the PCA space, while HOSVD is used for 3-D models. Within, the PCA space, linear regression (or interpolation) is used to reduce data in PCA space. The reduced data in the PCS is then recombined to form a reduced data of the permeability dataset.

Results show that the permeability field data reduction can be specifically defined for the PDFCase and the PCA-LinReg Case but not for the ArithMeanCase and the HarmMeanCase. This is because the latter cases will produce the same permeability dataset irrespective of the coarser resolution. The PCA-LinReg Case is the only technique that does not require a prior knowledge of blocks with similar permeability distribution before upscaling. This is a lareg advantage as it saves time during data pre-processing stages because sorting and calculations for each distinct region is avoided.
